### 2013-02-14 doc/xps2013/proposal.tex
edits all over

\paragraph{Curriculum development activities:} Concurrent with the execution of the research activities described in this grant we will seek to teach an advanced graduate class on advanced concurrency concepts.  We taught a similar class over six years ago and it is time to revive, update and teach it to the next generation of computer architecture graduate students.  \comment{Add more here.  This has no passion. -Mark}

@@

\vspace{1ex}
\noindent\textbf{Year 3:} In the third and final year of this effort (supported by this grant), we will finish the networking layer rewrite.  We will also have constructed a test-bed system comprised of mainly SSD-based memory.  Grappa will be ported to this new style of memory, which we envision will largely be a tuning and not rewriting effort.  We will explore alternative SSD-memory designs largely through emulation.  Finally we will complete a detailed system evaluation using our benchmark suite.

@@

The PIs organize their joint research activity under the umbrella of
the ``SAMPA group'' (SAfe MultiProcessing Architectures).  Some brief
statistics help summarize the group's size, strength, and focus:
\begin{itemize}
\item There are roughly ten graduate students, most actively
  coadvised.
\item In the last four years, the group has produced twelve papers
  published in ASPLOS, ISCA, PLDI, OOPSLA, MICRO, and OSDI as well as three
  papers in the USENIX Workshop on Hot Topics in Parallelism.
\end{itemize}
The SAMPA group is an ideal size for collaboration across the system
execution stack from computer architecture up through software
engineering.  Compared to large collaborations with several faculty,
there are no graduate students (or faculty) who specialize entirely in
particular subtopics.  The students gain expertise across
computer-science disciplines and use appropriate ideas from hardware,
software, theory, etc. to solve research problems.

>>>>

\paragraph{Curriculum development activities:} Concurrent with the execution of the research activities described in this grant we will seek to teach an advanced graduate class on advanced concurrency concepts.  We taught a similar class over six years ago and it is time to revive, update and teach it to the next generation of computer architecture graduate students. We will also reach out to instructors of classes that relate to large-scale irregular computation, e.g., machine learning and computer vision, in order to expose students to parallel programming concepts as well as the Grappa framework.

@@

\vspace{1ex} 
\noindent\textbf{Year 3:} In the third and final year of this
effort (supported by this grant), we will finish the networking layer rewrite.
We will also have constructed a test-bed system for the SSD-only data
structure research. Grappa will be ported to this new style of memory
hierarchy, which we envision will largely be a tuning and not rewriting
effort. Finally we will complete a detailed system evaluation using our
benchmark suite.

@@

The PIs organize their joint research activity under the umbrella of
the ``SAMPA group'' (SAfe MultiProcessing Architectures).  Some brief
statistics help summarize the group's size, strength, and focus:
\begin{itemize}
\item There are roughly ten graduate students, most actively
  coadvised.
\item In the last five years, the group has produced fifteen papers
  published in ASPLOS, ISCA, PLDI, OOPSLA, MICRO, and OSDI as well as three
  papers in the USENIX Workshop on Hot Topics in Parallelism.
\end{itemize}
The SAMPA group is an ideal size for collaboration across the system
execution stack from computer architecture up through software
engineering.  Compared to large collaborations with several faculty,
there are no graduate students (or faculty) who specialize entirely in
particular subtopics.  The students gain expertise across
computer-science disciplines and use appropriate ideas from hardware,
software, theory, etc. to solve research problems.
